Applying LIME to Bullet Data Journal

### 2018-12-14 journal/applying LIME to bullet data journal.Rmd
small changes

In order to assess which lime implementation is doing the best job of capturing the predictions from the random forest model, I decided to calculate the mean squared error for each of the input situations. I defined the mean squared error as 
  $$\frac{\sum_{i=1}^n (\hat{p}_{\mbox{simple}}-\hat{p}_{\mbox{complex}})^2}{n}$$
where $n$ is the number of observations in the testing dataset (within a set). Additionally, I was curious to compare the fits of the ridge regression models across input values, so I calculated the average $R^2$ for each input situation.

@@

>>>>

In order to assess which lime implementation is doing the best job of capturing the predictions from the random forest model, I decided to calculate the mean squared error for each of the input situations. I defined the mean squared error as 
  $$\frac{\sum_{i=1}^n (\hat{p}_{\mbox{simple},i}-\hat{p}_{\mbox{complex},i})^2}{n}$$
where $n$ is the number of observations in the testing dataset (within a set). Additionally, I was curious to compare the fits of the ridge regression models across input values, so I calculated the average $R^2$ for each input situation.

@@

```{r}
library(rpart)

tree <- rpart(samesource ~ ccf, data = hamby173and252_train, 
              control = rpart.control(cp = 0.0005, maxdepth = 2))
plot(tree)
text(tree)

tree2 <- cutree(tree, k = 5)
```
